---
title: "Mathematical Proof"
author: "John Shea"
date: "12/27/2018"
output: pdf_document
---

```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(echo = TRUE)
csv <- read.csv("~/projects/snhu/proof/proof-1-Q3.csv")
```

## Assignment \#1

1.
    a. $A \land B$
    b. Can be either:
        - $\neg A \land \neg B \land C$
        - $\neg (A \lor B) \land C$
    c. $(A \land C) \lor (B \land \neg C)$
    
\bigskip

2.
    a. Can be either:
        - Either Doug is tall and Eddie is short, or Doug is not tall.
        - Either Doug is not tall, or and Doug is tall and Eddie is short
    b. Future.
    
\bigskip
    
3.
```{r, echo=FALSE}
cols <- c("$G$", "$H$", "$L$", "$G \\lor \\neg H$", "$\\neg (G \\land H)$", "$(G \\lor \\neg H) \\land \\neg(G \\land L)$")
kable(csv, col.names=cols, booktabs=TRUE, align='cccccc')
```


\bigskip

4.

\bigskip

5.
|future|table|
|---|---|
|T | F|
    a. regular
    b. contradiction
        - Because the only connective used is the and (i.e. $\land$) operator, the
          parentheses are unneccessary. When those are removed, it is apparent that
          all of the individual terms (i.e. $M, \neg N, \neg M, N$) need to be true.
          Therefore both $M$ and $\neg M$, as well as, both $N$ and $\neg N$ are
          required to provied an answer of True. Both of those are contradictions
          and therefore either of those would be enought to render the statement a
          contradiction. 
    c. tautology
        - 
          
\bigskip

6.
    a. $Q \land P$
    b. $P \land \neg R$
