---
title: "Mathematical Proof"
author: "John Shea"
date: "`r format(Sys.time(), '%B %d, %Y')`"
fontsize: 12pt
output:
  pdf_document:
    extra_dependencies:
      - "makecell"
      - "booktabs"
      - "venndiagram"
---

\newcommand\such{\ |\ }

```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(echo = FALSE)
question_three <- read.csv("~/projects/snhu/proof/question_three.csv")
question_four <- read.csv("~/projects/snhu/proof/question_four.csv")
question_five_prelim <- read.csv("~/projects/snhu/proof/question_five_prelim.csv")
question_five_conclusion <- read.csv("~/projects/snhu/proof/question_five_conclusion.csv")
```

# Assignment \#2

## Question 1

a. Any of:
    - {x | x is a positive integer that is divisible by 5}
    - {$x \in \mathbb{Z}^+ \such 5 \mid x$}
    - {$5x \such x \in \mathbb{Z}^+$}

b. Any of:
    - {x | x is an integer between -4 and 3 inclusive}
    - {$x \in \mathbb{Z} \such -4 \le x \le 3$}

c. Any of:
    - {x | x is a prime number}
    - {$x \such \pi(x)$}

## Question 2

a.

\begin{minipage}[t]{0.4\linewidth}
\begin{center}
$A \cap B$\\
\begin{venndiagram3sets}
  \fillACapB
\end{venndiagram3sets}
\end{center}
\end{minipage}
\begin{minipage}[t]{0.4\linewidth}
\begin{center}
$(A \cap B) \setminus C$ (i.e. $A \cap B$ remove C)\\
\begin{venndiagram3sets}
  \fillACapBNotC
\end{venndiagram3sets}
\end{center}
\end{minipage}

\begin{minipage}[t]{0.4\linewidth}
\begin{center}
$A \setminus C$\\
\begin{venndiagram3sets}
  \fillANotC
\end{venndiagram3sets}
\end{center}
\end{minipage}
\begin{minipage}[t]{0.4\linewidth}
\begin{center}
$B \setminus C$\\
\begin{venndiagram3sets}
  \fillBNotC
\end{venndiagram3sets}
\end{center}
\end{minipage}

b.

\begin{minipage}[t]{0.4\linewidth}
\begin{center}
$A \setminus B$\\
\begin{venndiagram3sets}
  \fillANotB
\end{venndiagram3sets}
\end{center}
\end{minipage}
\begin{minipage}[t]{0.4\linewidth}
\begin{center}
$C \cup (A \setminus B)$ (i.e. $A \setminus B$ add C)\\
\begin{venndiagram3sets}
  \fillOnlyA \fillC
\end{venndiagram3sets}
\end{center}
\end{minipage}

## Question 3

\begin{minipage}[t]{0.4\linewidth}
\begin{center}
$A \setminus B$\\
\begin{venndiagram3sets}
  \fillANotB
\end{venndiagram3sets}
\end{center}
\end{minipage}
\begin{minipage}[t]{0.4\linewidth}
\begin{center}
$C \cup (A \setminus B)$ (i.e. $A \setminus B$ add C)\\
\begin{venndiagram3sets}
  \fillOnlyA \fillC
\end{venndiagram3sets}
\end{center}
\end{minipage}

## Question 4

a. $W \rightarrow (S \land \lnot M)$
b. $(W \land \lnot M)\rightarrow S$
c. $W \rightarrow (S \land \lnot M)$

### Explanation

- b and e are equivalent
    - using the distribution law, $e$ become $(K \lor J) \land (K \lor \neg K)$
    - $K \lor \neg K$ is a tautology, therefore the above statement is equivalent to
      $J \lor K$, which is statement $b$
- c and d are equivalent
    - using DeMorgan's law, $d$ becomes $\neg\neg J \lor \neg K$
    - using the Double Negation law, the above statement becomes $J \lor \neg K$,
      which is $c$

## Question 5

### Preliminaries

```{r}
cols <- c("\\thead{\\\\$M$}", "\\thead{\\\\$N$}",
          "\\thead{\\\\$M \\land \\neg N$}",
          "\\thead{\\\\$\\neg M \\land N$}",
          "\\thead{\\\\$\\neg M \\lor N$}",
          "\\thead{\\\\$\\neg M \\lor N$}")
kable(question_five_prelim, col.names=cols, booktabs=TRUE, align='cccccc')
```

### Conclusion

```{r}
cols <- c("\\thead{a\\\\ $(M \\land \\neg N) \\lor (\\neg M \\land N)$}",
          "\\thead{b\\\\ $(M \\land \\neg N) \\land (\\neg M \\land N)$}",
          "\\thead{c\\\\ $(\\neg M \\land \\neg N) \\lor (\\neg M \\lor N) \\lor (M \\land \\neg N)$}")
kable(question_five_conclusion, col.names=cols, booktabs=TRUE, align='ccc')
```

### Explanation

\begin{center}
\begin{venndiagram3sets}[labelOnlyA={1},
                         labelOnlyB={2},
                         labelOnlyC={3},
                         labelOnlyAB={4},
                         labelOnlyAC={5},
                         labelOnlyBC={6},
                         labelABC={7},labelNotABC={8}]
\fillACapC
\end{venndiagram3sets}
\end{center}
          
## Question 6

a. $Q \land P$
b. $P \land \neg R$
