---
title: "Mathematical Proof"
author: "John Shea"
date: "January 21, 2019"
fontsize: 12pt
output:
  pdf_document:
    extra_dependencies:
      - makecell
      - booktabs
      - float
      - venndiagram
---

\newcommand\such{\ |\ }

```{r setup, include=FALSE}
library(knitr)
library(kableExtra)
knitr::opts_chunk$set(echo = FALSE)
question6a <- read.csv("question6a.csv", colClasses="character")
question5a <- read.csv("question5_a.csv", colClasses="character")
question5b <- read.csv("question5_b.csv", colClasses="character")
question5c <- read.csv("question5_c.csv", colClasses="character")
```

# Assignment \#2

## Question 1

a. Any of:
    - {x | x is a positive integer that is divisible by 5}
    - {$x \in \mathbb{Z}^+ \such x \equiv 0\ (\textrm{mod 5})$}
    - {$x \in \mathbb{Z}^+ \such 5|x$}
    - {$5x \such x \in \mathbb{Z}^+$}

b. Any of:
    - {x | x is an integer between -4 and 3 inclusive}
    - {$x \in \mathbb{Z} \such -4 \le x \le 3$}

c. Any of:
    - {x | x is a prime number}
    - {$x \such \pi(x)$}

## Question 2

a. \input{question2a.tex}

b. \input{question2b.tex}

## Question 3

\input{question3.tex}

### Explanation

\input{question3_explanation.tex}

## Question 4

a. $W \rightarrow (S \land \lnot M)$
b. $S \rightarrow (W \land \lnot M)$
    - This statement is different than a and c in that it specifies what
      conditions can be determined from the knowledge that I will go shopping.
      While a and c detail what information can be gleaned from the information
      that I will go shopping.
c. $W \rightarrow (S \land \lnot M)$
    - equivalent to statement a. Both statements allow for the conclusion that
      I will got shopping and I will not go to a movie based on the information that
      it is Wednesday.

## Question 5

\input{question5.tex}

This can also be shown with truth tables.

### $P \leftrightarrow Q$

```{r}
cols <- c("\\thead{$P$}", "\\thead{$Q$}", "\\thead{$P \\rightarrow Q$}",
          "\\thead{$Q \\leftarrow P$}", "\\thead{$P \\leftrightarrow Q$}")
kable(question5a, "latex", escape=F, col.names=cols,
      booktabs=T, align='ccccc', linesep='') %>%
  kable_styling(position = "center")
```


### $\lnot P \leftrightarrow \lnot P$

```{r}
cols <- c("\\thead{$\\lnot P$}", "\\thead{$\\lnot Q$}",
          "\\thead{$\\lnot P \\rightarrow \\lnot Q$}",
          "\\thead{$\\lnot Q \\leftarrow \\lnot P$}",
          "\\thead{$\\lnot P \\leftrightarrow \\lnot Q$}")
kable(question5b, "latex", escape=F, col.names=cols,
      booktabs=T, align='ccccc', linesep='') %>%
  kable_styling(position = "center")
```

### $P \leftrightarrow Q \land \lnot P \leftrightarrow \not Q$

```{r}
cols <- c("\\thead{$P$}", "\\thead{$Q$}",
          "\\thead{$P \\leftrightarrow Q$}",
          "\\thead{$\\lnot P \\leftrightarrow \\lnot Q$}")
kable(question5c, "latex", escape=F, col.names=cols,
      booktabs=T, align='cccc', linesep='') %>%
  kable_styling(position = "center")
```
 
## Question 6

a. $P \lor Q \equiv \neg P \rightarrow Q$
    - By the rules of implication, $\neg P \rightarrow Q$ will be true whenever $P$
      is true. This accounts for the left side of the statement $P \lor Q$. When
      $P$ is false, the implication requries $Q$ to be true in order to be a
      true statement (which is the conditional law), thus perfectly replicating
      the original disjunct term, as the folowing truth table demonstrates.

```{r}
cols <- c("\\thead{$P$}", "\\thead{$Q$}", "\\thead{$P \\lor Q$}",
          "\\thead{$\\neg P \\rightarrow Q$}")
kable(question6a, "latex", escape=F, col.names=cols,
      booktabs=T, align='cccc', linesep='') %>%
  kable_styling(position = "center")
```

b. $P \land Q \equiv \neg(P \rightarrow \neg Q)$
    - The $\neg$ on the outside of the parenthesis reverses the meaning of the inside
      term (i.e. $P \rightarrow Q$). Therefore, to make this statement equivelant to
      $P \land Q$, this statement needs to return fase only when P and Q are both true.
      $P \leftarrow Q$ will return true whenever P is false, so this gaurentees
      that P must be true. By setting the right-hand side of the implication to
      $\neg Q$, This gaurantees that if $P$ is true and Q false $P \rightarrow Q$
      will return true. Therefore, the only way the inside statement fails is if
      $P$ and $Q$ are both true. Thus return a true for the overall statement.
      This is best demonstrated with the following equivalences:

      \input{question6b.tex}

